### 2018-11-13 ms/ms_prosop.tex
updated tex

\subsubsection*{Ethics approval and consent to participate}
\small{All participants gave informed consent before taking part in the experiment, which was approved by the ethics board of Bielefeld University (ethics statement 2016-133).} \\

\subsubsection*{Data Availability}   
\small{
	fMRI results maps are available on \\
	\href{https://neurovault.org/collections/4017/}{neurovault.org/collections/4017}  \\
	Code to reproduce the results and figures, as well as to recreate this manuscript, can be found on  \\
	\href{https://doi.org/10.5281/zenodo.1485911}{doi.org/10.5281/zenodo.1485911}.  
}

@@

\subsubsection*{Copyright}
\small{
	(C)2018 Wegrzyn et al. This article is distributed under the terms of the \href{http://creativecommons.org/licenses/by/4.0/}{Creative Commons Attribution License}, which permits unrestricted use, distribution, and reproduction in any medium, provided the original authors are credited.  
}

>>>>

\subsubsection*{Ethics approval and consent to participate}
\small{All participants gave informed consent before taking part in the experiment, which was approved by the ethics board of Bielefeld University (ethics statement 2016-133).}

\subsubsection*{Data Availability}
\small{
	fMRI results maps are available on \\
	\href{https://neurovault.org/collections/4017/}{neurovault.org/collections/4017}  \\
	Code to reproduce the results and figures, as well as to recreate this manuscript, can be found on  \\
	\href{https://doi.org/10.5281/zenodo.1485911}{doi.org/10.5281/zenodo.1485911}.}

@@

\subsubsection*{Copyright}
\small{
	(C)2018 Wegrzyn et al. This article is distributed under the terms of the \href{http://creativecommons.org/licenses/by/4.0/}{Creative Commons Attribution License}, which permits unrestricted use, distribution, and reproduction in any medium, provided the original authors are credited.}
